Untitled

### 2024-02-05 MSR.rmd
Update

@@

>>>>

```{r}
x0 <-78 
n <- 250
a <- 1598
b <- 17
m <- 1000

@@

# Bab 3

![](images/clipboard-2906850533.png){width="302"}

## Bernoulli

![](images/clipboard-1833550608.png){width="391"}

```{r}
#Bernouli
i <- 1000
p <- .65
X <- runif(i)
Y <- NULL
for (z in 1:i) ifelse (X[z] <= p, Y[z] <- 1, Y[z] <- 0)
(tabel <- table(Y)/length(Y))
barplot(tabel, main="Bernoulli")

i <- 1000
p <- .65
X <- runif(i)
Y <- (X <= p)+0
(tabel <- table(Y)/length(Y))
barplot(tabel, main="Bernoulli")
```

## Seragam Diskrit

![](images/clipboard-958172702.png){width="443"}

```{r}
i<-1000 
N<-4
X<-runif(i) 
DU<-NULL
for (z in 1:i){
if (X[z]<=1/N) DU[z]<-1
else if (X[z]<=2/N) DU[z]<-2  
else if (X[z]<=3/N) DU[z]<-3
else DU[z]<-4 
}
(tabel<-table(DU)/length(DU)) 
barplot(tabel,main="Seragam Diskret")
```
